---
title: "LA_4"
author: "Adam Hayes, Erin Omyer, Jasmine Sanchez, and Richard Park"
date: "2/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, se = FALSE)
```

```{r}
library(tidyverse)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = `bwt/oz`)
babies <- na.omit(babies)
babies
```

###Questions and Importance
1. Do mothers who smoke have increased rates of premature delivery?
2. Are newborns from mothers who smoke more likely to have smaller birthweights at every gestational age?

These questions are important because in this day and age, with so much new medical information and statistics people are much more concerned with pregnant mothers smoking than they were even 50 years ago.  It is now a widely accepted opinion that women who are pregnant should not smoke, so it is interesting to investigate the actual effects on the newbors for women who smoke during pregnancy vs. those who don't smoke.


```{r}
ggplot(data = babies) +
  geom_bar(mapping = aes(x = Premature, y = ..prop.., group = 1, fill = smoke))+
  facet_wrap(~smoke)+
  labs(title = "Premature Births for those who Smoke During Pregnancy vs. Those Who Don't")

ggplot(data = babies)+
  geom_point(mapping = aes(x = gestation, y = bwtoz, color = smoke))+
  facet_wrap(~time)+
  geom_smooth(mapping = aes(x = gestation, y = bwtoz),se = FALSE)+
  labs(title = "Birthweight & Gestation length for Smokers vs. Nonsmokers")
```
###Question Conclusion
1. Mother's who smoke during pregnancy, in comparison, to mother's who don't smoke share similar findings. In our study, we created a bar graph between the two variables, resembling the weak correlation between smoking and not smoking during pregnancy. From the data, people who smoke during pregnancy have a slight higher chance of premature births. 
2. In our second graph, we created a scatterplot between gestational age and the weight of the baby when born. From our visualization, the relationship between smokers and non-smokers for the two variable share similar results. As gestation age increases, the weight of the baby increases. From the graph, smokers have a higher weight of birth as the gestational age increases. But, the data is similar to each other, so the correlation isn't strong. 
```{r}
ggplot(data = babies) + geom_point(mapping = aes(x = mht, y = bwtoz), color = "blue", position = "jitter") + geom_smooth(mapping = aes(x = mht, y = bwtoz), color = "pink") + facet_wrap(~ time) + labs(title = "Mother's Height compared with Birthweight of Their Baby")
```

###Erin's Findings
I, Erin Omyer, created a scatterplot between the Mother's height in comparison to the birth weight of their baby, but including the overall outlook at the number of times the mother has smoked. In the graph on the left, it shows the mother's that haven't ever smoked, showing a pattern of generally an average birth weigth. But, when you look at as the number of cigarettes a person smokes in a day, then the birth weight dropped. By displaying the scatterplot with the smooth line, it allows viewers to see the pattern easier with the line and the high number of people among the sample.

```{r}
ggplot(data = babies) +
  geom_point(mapping = aes(x = bwtoz, y = number, color = Premature)) + labs(title = "Birthweight compared with # of Cigarettes Smoked by Mother")

```

###Jasmine's Findings:
I found that by comparing the birthweights of babies to the number of cigarettes smoked a day for current and past smokers,there is a pattern that may become apparent while analyzing the prematurity of those births. There is a clear distinction between the number of birth weights recorded as the number of cigarettes smoked per day increases. Now including the premature factor; premature birth is typically associated lower birth weights, this graph supports that because we can see the color differentiation between premature births and births carried to term. I noticed that the increase in births carried to term were most common in non-smokers. However, the one distinction would be where we see a larger grouping of moderate birthweights with smokers who reported smoking 5 cigarettes a day. This information led me to see the decrease in premature weights as well with past smokers.

```{r}
ggplot(data = babies)+
  geom_point(mapping = aes(x = bwtoz, y = mpregwt))+
  geom_smooth(method = loess, mapping = aes(x = bwtoz, y = mpregwt), se = FALSE)+
  facet_wrap(~smoke)+
  labs(title = "Babies body weight in ounces versus mother's pregnancy weight")
```

###Richard's Findings
I, Richard Park, created a scatterplot comparing the Mother's pregnancy weight and the babies body weight (in ounces) at birth. I divided the graph into two seperate facets to help me compare mothers who smoked versus mothers who didn't smoke. In the graph containing the mothers who smoked(AKA the side labeled 1), my trendline showed that the babies birth weight eventually levels after the mother's pregnancy weight reaches a little over 130 pounds. However, in the graph containing the mothers who didn't smoke, the trendline never levels off at any point. For the first half, both trendlines closely resembled each other and both had a negative slope. This suggests that smoking might have an affect on a babies birth weight when the mother's pregnancy weight reaches 130 pounds, meaning babies can't get bigger/heavier after this threshold.

###Overall Contribution
As a team, we divided the work up evenly among all of us. For the team graph, Adam and Richard worked together to create a visualization to answer the two questions. Then, Erin answered the findings from the graph, then Jasmine provided the recommendation from our findings. Everyone completed their individual parts on their own and submitted to the lab. Richard asnwered the preliminary conclusion from Adam's visualization that he formed. 